### Information of Project Details
    title: "Leaflet"
    author: "Brenda M. Balala"
    date: "December 31, 2018"
    output: html_document
    always_allow_html: yes
---


## Introduction
  
  Leaflet is one of the most popular Javascript libraries for
creating interactive maps. The leaflet R package allows you
to create your own leaflet maps without needing to know any
Javascript!
  
### Installation
  
  ```{r, eval=TRUE}
#install.packages("leaflet")
library(leaflet)
```

## My first leaflet map

```{r, echo=TRUE}
library(leaflet)

## Latitude and Longitude of South Cotabato map where pineapple is planted

bmb    <- data.frame( lat = c(6.4974,6.3385, 6.1164, 6.1400, 6.2245)
                       , lng = c(124.8472,124.9727, 125.1716, 124.9060, 125.0608) )
## Pineapple Popups

pineapplePopups <- c(
  "<a href='https://www.koronadal.gov.ph/'>Koronadal City</a>",
  "<a href='http://southcotabato.gov.ph/city-municipalities/tupi/'>Tupi</a>",
  "<a href='http://go.gensantos.gov.ph/'>General Santos City</a>",
  "<a href='http://tboli.globalmatters.com/'>T'boli</a>",
  "<a href='http://southcotabato.gov.ph/city-municipalities/polomolok/'>Polomolok</a>"
)
setwd("D:/shiny/wk2")
pineappleIcon <- makeIcon("pineapple.png", 30, 30) 

mp <- bmb %>% 
  leaflet() %>%
  addTiles() %>% setView(lng = 124.8472, lat = 6.2245,  zoom = 10) %>% 
  addMarkers(icon=pineappleIcon, popup = pineapplePopups)
mp
```


## Conclusion
            
            For more details about the leaflet package for R 
            visit http://rstudio.github.io/leaflet/.